### 2004-05-19 Documentation/part2.tex
*** empty log message ***

The set of rules\index{Rule} for an experiment is the final 
link between the event rate
computation and the statistical analysis. The information given by the rules
specifies how the $\chi^2$ is computed based on the raw event rates as 
described by the channels including possible systematical errors. 
Therefore a rule has two parts: the first part describes how signal and 
background events are composed out of the channels and the second part
specifies which systematical errors are considered and what the size
of the relevant errors is.

Based on the definition of channels it is possible to assemble the 
signal and background event numbers for each bin.  
The signal $s_i$ in one bin for a rule now can be composed out of 
several channels by
\begin{equation}
s_i=\epsilon_{c_1}\cdot n_i^{c_1}\,+\,\epsilon_{c_2}\cdot n_i^{c_2}\,+\,\ldots
\end{equation}
where the $\epsilon$'s are weight factors determined by the properties
of the detector.
Similarly the background in one bin $i$ can be specified by
\begin{equation}
b_i=\epsilon_{c_1}\cdot n_i^{c_1}\,+\,\epsilon_{c_2}\cdot n_i^{c_2}\,+\,\ldots
\end{equation}
This basic building blocks of a rule are specified by
\begin{quote}
{\tt \tb @signal = 0.5 @ \#channel\_1\\
\tb @background = 0.001 @ \#channel\_2 :  0.005 @ \#channel\_3
}
\end{quote}

>>>>

The set of rules\index{Rule} for an experiment is the final 
link between the event rate computation and the statistical analysis. 
The information in the rules
specifies how the $\chi^2$ is computed based upon the raw event rates 
given by the channels and possible systematical errors. 
Therefore a rule has two parts: The first part describes how signal and 
background events are composed out of the channels, and the second part
specifies which systematical errors are considered, as well as their values.
%
For a rule, the splitting
in signal and background is useful for simplicity and the treatment of systematics, as we will se later. Each rule will lead to a $\chi^2$-value,
which means that all $\chi^2$'s of the different rules will be added
for the whole experiment. Within each rule, the event rates are added, and
the systematics is considered to be independent of the other rules.
Thus, it is convenient to combine the above defined channels for different
oscillation patterns and interaction types into one logical construction,
which is the rule. For example, a superbeam usually has two rules: One for
the $\nu_e$-appearance rates, and one for the $\nu_\mu$-disappearance rates.
 In each case, contributions of several interaction types, as well as from
 the $\nu_e$-contamination of the beam will lead to a number of contributing signal and background event channels.

% WEITER:

Based on the definition of channels it is possible to assemble the 
signal and background event numbers for each bin.  
The signal $s_i$ in one bin for a rule now can be composed out of 
several channels by (OFTEN ONLY ONE) 
\begin{equation}
s_i=\epsilon_{c_1}\cdot n_i^{c_1}\,+\,\epsilon_{c_2}\cdot n_i^{c_2}\,+\,\ldots
\end{equation}
where the $\epsilon$'s are weight factors determined by the properties
of the detector.
Similarly the background in one bin $i$ can be specified by
\begin{equation}
b_i=\epsilon_{c_1}\cdot n_i^{c_1}\,+\,\epsilon_{c_2}\cdot n_i^{c_2}\,+\,\ldots
\end{equation}
This basic building blocks of a rule are specified by
\begin{quote}
{\tt \tb @signal = 0.5 @ \#channel\_1\\
\tb @background = 0.001 @ \#channel\_2 :  0.005 @ \#channel\_3
}
\end{quote}
